Canonical rings of log spin stacky curves

### 2015-07-08 curves-write-up/spin_cring.tex
dk edits

\begin{rem}
\label{rem:gen-at-most-three}
If $M(\Gamma)$ has some odd weight modular form, then it has an odd weight modular form in weight $3$. When $g \geq 2$, we see that this is true because $\dim_k H^0(\sx, 3\halfcan) > 0$ by Riemann--Roch and the fact that $\deg \lfloor 3\halfcan \rfloor > 2g - 1$. When the genus is zero or one, we see that there is a generator in weight $1$ or weight $3$ in the base cases given in Table ~\ref{table:g-1-base} and Table ~\ref{table:g-0-base-cases}. Hence, there is an odd weight modular form in weight $3$ in general. A consequence of this observation is that the bound on the degree of generators and relations when $M(\Gamma)$ has some odd weight modular form, as given in Corollary ~\ref{cor:main-mod-forms}, is closely related to the degree of the minimal odd weight modular form.
\end{rem}

@@

\noindent
Thus, there exist rational sections $t_i$ of $\sco(\lfloor k \halfcan \rfloor)$ with $\ord_P^{L'}(t_i) = i$
for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
\beta} \rfloor \}$. We will the use positive best lower approximations to
construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.

Let 
\[
	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
	\beta}
\]

>>>>

\begin{rem}
\label{rem:gen-at-most-three}
If $M(\Gamma)$ has some odd weight modular form, then it has an odd weight modular form in weight $3$. When $g \geq 2$, we see that this is true because $\dim_\Bk H^0(\sx, 3\halfcan) > 0$ by Riemann--Roch and the fact that $\deg \lfloor 3\halfcan \rfloor > 2g - 1$. When the genus is zero or one, we see that there is a generator in weight $1$ or weight $3$ in the base cases given in Table ~\ref{table:g-1-base} and Table ~\ref{table:g-0-base-cases}. Hence, there is an odd weight modular form in weight $3$ in general. A consequence of this observation is that the bound on the degree of generators and relations when $M(\Gamma)$ has some odd weight modular form, as given in Corollary ~\ref{cor:main-mod-forms}, is closely related to the degree of the minimal odd weight modular form.
\end{rem}

@@

\noindent
Thus, there exist rational sections $t_i$ of $\sco(\lfloor k \halfcan \rfloor)$ with $\ord_P^{L'}(t_i) = i$
for any $i \in \{0, \ldots, \lfloor k \frac{\alpha}{
\beta} \rfloor \}$. We will the use positive best lower approximations to
construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.

Let 
\[
	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{
	\beta}
\]
